Gravitational wave sources in our Galactic backyard: Predictions for BH and NS binaries in LISA

### 2021-07-06 paper/tex/sections/results.tex
lieke feedback section 3.1

We show the expected distribution of detectable DCOs together with the LISA sensitivity curve in Figure~\ref{fig:dcos_on_sc}. This shows that the detectable population of these massive DCOs is concentrated at comparatively lower frequencies than the LISA verification binaries (shown as stars in the top panel). This is expected since producing the same SNR as a BHBH, BHNS or NSNS with a relatively lower mass (circular) WDWD requires a higher frequency. This finding is in agreement with \citet{Sesana+2020} and as noted in that work, this could possibly be used to distinguish these more massive DCOs from WDWDs probabilistically. There are several other notable features in these distributions and to understand these we overplot reference lines indicating where a circular binary with the average chirp mass (annotated in each panel) would reside for a given remaining inspiral time (vertical lines) and a given distance (diagonal lines).

We would expect that if a population was entirely circular, it should be bounded approximately between the $0.1$--$30 \unit{kpc}$ lines (roughly the minimum and maximum distance to a source in the Milky Way). From inspection of the bottom panels with each individual DCO type we see that, though this is the true for a large fraction of the population, there is a distinct subpopulation of binaries that extend downwards, especially around $2 \unit{mHz}$. This offshoot is composed of eccentric binaries for which the circular distance contours do not apply. For instance, we plot the 90\% contour of only the circular sources in our sample over the density distribution in each of the bottom panels and it is clear that the circular subsample is bounded by the distance lines. We also plot a line of constant distance at $30 \unit{kpc}$ for an eccentric binary with $e = 0.98$ to show the differences for eccentric sources. Additionally, we note that the peak of the density distribution coincides with the centre of the Milky Way as expected, since binaries are most likely to be formed towards the centre of the Galaxy.

>>>>

We show the expected distribution of detectable DCOs together with the LISA sensitivity curve in Figure~\ref{fig:dcos_on_sc}. This shows that the detectable population of these DCOs is concentrated at comparatively lower frequencies than the LISA verification binaries (shown as stars in the top panel). This is expected since producing the same SNR as a BHBH, BHNS or NSNS with a relatively lower mass (circular) WDWD requires a higher frequency. This finding is in agreement with \citet{Sesana+2020} and as noted in that work, this could possibly be used to distinguish more massive DCOs from WDWDs probabilistically. There are several other notable features in these distributions. To understand these we overplot reference lines indicating where a circular binary with the average chirp mass ($\avg{\mathcal{M}_c}$, annotated in each panel) would reside for a given remaining inspiral time (vertical lines) and a given distance (diagonal lines).

Firstly, we note that the peak of the density distribution coincides with the centre of the Milky Way as expected, since binaries are most likely to be formed towards the centre of the Galaxy. Additionally, we expect that if a population is entirely circular, it should be bounded approximately between the $0.1$--$30 \unit{kpc}$ lines, roughly the minimum and maximum distance to a source in the Milky Way. From inspection of the bottom panels with each individual DCO type we see that this is the true for a large fraction of the population. However, there is a distinct subpopulation of binaries that extend downwards, especially around $2 \unit{mHz}$. This offshoot is composed of eccentric binaries for which the circular distance contours do not apply. For instance, we plot the 90\% contour of only the \textit{circular} sources in our sample over the density distribution in each of the bottom panels and it is indeed bounded by $0.1$--$30 \unit{kpc}$ the distance lines. We also plot a line of constant distance at $30 \unit{kpc}$ for an eccentric binary with $e = 0.98$ to show the different limit for eccentric sources. To further illustrate this point, we show the same plot but with each point coloured by its eccentricity in Fig.~\ref{fig:dcos_on_sc_ecc_col}. Overall, we can see that eccentric sources tend to be located on a slightly different location on the sensitivity curve and so this could perhaps be used help in identifying them.
